Hydra Battles and Cie

### 2021-01-25 doc/part-hydras.tex
add an exercise

\index{Exercises}
 \begin{exercise}
Let $\alpha$ be an ordinal. We say that $\alpha$ is \emph{infinite} iff the segment $[0,\alpha)$ is an infinite set. 
\begin{enumerate}
\item Adapt this definition to the type \texttt{E0}.
\item Prove that \emph{being infinite} is decidable on type \texttt{E0}.
\item Prove that $\alpha$ is infinite if and only if for any finite ordinal $i$,
$i+\alpha=\alpha$.
\end{enumerate}
 \end{exercise}

>>>>

%% To simplify !
\index{Exercises}
\begin{exercise}
Prove that for any ordinal $\alpha:\texttt{E0}$, 
$\omega\leq \alpha$ if and only if, for any natural number $i$,
$i+\alpha=\alpha$.

\emph{You may start this exercise with the file
\url{../exercises/ordinals/ge_omega_iff.v}.}
\end{exercise}
